\section*{Acknowledgements}

I would like to take a bit of time here and thanks all the people that have made this moment possible.

Quiero agradecerle a mi familia por apollarme y creer en mi durante este tiempo. A mi mama, Luisa Medina por siempre estar pendiente de me. Siempre buscandome aunque a vecese sea dificil contacterme conmigo. Gracias por no rendirte y seguir tratando. A mi papa, Carlos Sanchez, gracias por los sacrificios que hisiste para que nosotros tuvieramos mas oportunidades y hacer esa fundacion para yo poder llegar a donde estoy hoy.
A mi hermana Ana Solano, 
A mi hermana Yafreisy Scarle,
A mi hermano Carlos Sanchez,
A mi sobrinos y sobrinas Miracle, Valdi, Amaya, Eva y Noah

To Chris Tunnell
To Erszebet Merenyi

Id like to thank my friends from my cohort: 
Diego Fallas
Dale Lowder
Mason, Sohail, Visal Jonathan

Edith Sophia Bahamon Farfan, thank you for being such an amazing friend, I count myself lucky for being able to meet you and even more so us developing this friendship. Thanks for helping me through so many of my hardships and being on my side.
Patricio Zor
Mairana Garcia
Minoti
Yamikani Phiri

%maybe cut here individual names
Sonia
Miriam Gammers,
Julianne

Yamikani Phiri
Josue and Nilima
Rozena
Nkruma
Kerri

To all my friends at rice: Max, Esteban, Xiaoke

To my friends in the physics department: Max, Monica, Jonathan, Dashon, Collin
% End of cutting out names

To all my friends at Valhalla



In memory of Tanner.


Id like to thank my coworkers,
Ivy Li,
Dr. Dorian Amarale,
Dr. Juehang Qin,
Dr, Shixiao Liang,
To the undergrads that works on our group.

Id like to thank my collaborators in the XENON and XAMS experiments. None of this work would have been possible without your help
Lanquing,
Daniel Wez,
Sebastian Vetter,
Dacheng,
Johannes
And all other collaborators.

To my wonderful girlfriend Jennifer Mead



\textcolor{white}{Id like to thank Rose, thank you for being in my life. I wish you all the happiness in the world and more, i know you deserve it and dont ever doubt that. Forever and always.}